---
title: "individual1.Rmd"
author: "Rabsa Naseer"
date: "9/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. How are the ratings distributed? Create both a histogram and a boxplot and describe them. Don’t forget to mention outliers, if there are any.
```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco) 

ratings <- choco$Rating
boxplot(ratings)
hist(ratings)
```

It looks like there are outliers at 1.0, 1.5, and 1.75,looking at both the histogram and boxplot, were outliers are values that don't "fit in" with the rest of the data (indicated by individual dots in the boxplot).

2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports.

```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 

years <- choco$Date
barplot(table(years), main = "Ratings Per Year", xlab ="Year",  ylab = "# of Ratings")
```

3. Do ratings depend on the cacao percentage of a chocolate bar? Create both numerical and graphical summaries, and explain.

```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
cor(choco$Rating, choco$Cocoa_Percent)

plot(choco$Cocoa_Percent, choco$Rating)
abline(lm(choco$Rating ~ choco$Cocoa_Percent))
```

The correlation calculated shows an insignificant correlation coefficient. If there was a relationship between ratings and cocao percentage, negative or positive, the value would be 0.8 or greater or -0.8 or less. 
The plot shows no obvious trend in the data either. All the points are fairly random and distributed.

4. How do different characteristics of the chocolate compare? To elaborate, which characteristics tend to be more favorable and which ones are not? Create both numerical and graphical summaries, and explain.

```{r}

```

5. Brainstorm two analyses you would like to perform with your teammate. Describe in plain language what comparisons are you making. Create suitable numerical and graphical summaries for your analyses. Describe the results.

The one analysis I will be doing is grouping the ratings by the company that made each chocolate. Then compare companies and their average, mean, ratings. This will show if the company can effect or determine good or bad ratings.

```{r}

library("dplyr")
means <-  aggregate(choco$Rating, by=list(Company=choco$Company), FUN=mean)
rates <- means$x
names(rates) <- means$Company
top5 <- head(sort(rates, decreasing = TRUE), n= 5)
top5

```

